\cvsection{Honors \& Awards}
\begin{itemize}
    \item Invited at PRO TV (ILikeIT, a show where innovative apps are showcased)
\end{itemize}

\cvsection{Projects}
\cvproject{Divers Data and Drivers Data PRO}
\begin{itemize}
    \item Developed the first virtual logbook for drivers. Drivers Data is a serverless app that uses Firebase, Node.js, Java and was built for Android. The web version of the app is built with HTML, CSS and JS. The app can generate reports for up to 3 years, in just 15 seconds. Those reports are saved in an EXCEL table. More than 50 users daily, with a total of 1000 active users.
\end{itemize}
\cvproject{PBI}
\begin{itemize}
    \item Developed a web-app where students can find solutions to most of the problems shown by PbInfo. The website contains more than 1000 algorithms and solutions to the problems. For this web-app I used Firebase, C\#, React and HTML + CSS for some pages. More than 100 users daily.
\end{itemize}
\cvproject{RIP.WTF}
\begin{itemize}
    \item Developed a website to quickly shorten urls. The front end was made in React and the back end was written in Node.js. As a database I used a NOSQL database.
\end{itemize}
\cvproject{Whist Score Table}
\begin{itemize}
    \item Developed an app for the players of Whist. The app is a score-keeper and was written in Java, for Android. I also used Firebase Functions and Firestore. More than 200 players have used this app for their score-keeping.
\end{itemize}
\cvproject{MyGoal: Expenses Assistant}
\begin{itemize}
    \item Built an app that motivates the user to save money.
\end{itemize}
\cvproject{Music.me}
\begin{itemize}
    \item Build a native Android app that displays real-time data for the songs that is currently playing on the device. Used Java, XML and the last.fm api.
\end{itemize}
\cvproject{Guess The Song}
\begin{itemize}
    \item Developed a native Android game that challenges the user to guess a song based on the translated version of its lyrics. The app also has variations for less-popular song genres.
\end{itemize}
\cvproject{}

\cvsection{Volunteering}
\begin{itemize}
    \item Volunteered as Full Stack Software Developer at the VianuMUN website for the Vianu MUN conference in 2019.
    \item Volunteered as Assets Designer for "Concurs de Costume Traditionale Romanesti".
\end{itemize}